---
title: "Investigation of Central Limit Theorem"
author: "Pranjal Mandhaniya"
date: "Monday 22 January 2015"
output: html_document
---


- <b>Overview</b>

    In this project we will investigate the exponential distribution in R and compare it with the Central Limit Theorem. 

- <b>Simulations</b>

    We simulated it in R with rexp(n, lambda) where lambda is the rate parameter.Set seed to get always same result.Set lambda = 0.2.
    The mean of exponential distribution is <u>1/lambda i.e. 5(theoritical mean)</u> and the standard deviation is also <u>1/lambda i.e. 5.</u> 

```{r}
# 1000 averages of 40 generated random exponentials 
mns = NULL
set.seed(12)
for (i in 1 : 1000) mns = c(mns, mean(rexp(40,0.2)))
iid <- (mns-5)/(5/sqrt(1000)) # (sample mean-theoritical mean)/std. error

# 1000 generated random exponentials 
set.seed(12)
x <- rexp(1000,0.2)
iid2 <- x-5/(5/sqrt(1000))
```

- <b>Sample Mean versus Theoretical Mean</b>

    Perform t-test for mean comparisions 

```{r, echo=TRUE}
t.test(iid,iid2)
```

- <b>Sample Variance versus Theoretical Variance</b>
    Perform f-test for variance comparisions.
    
```{r}
var.test(iid,iid2)
```

- <b>Distribution</b>
    Draw histogram of 1000 averages of 40 PRGN exponentials
    
```{r}
hist(iid,50,col="red")   # barplot is centered arround 0 and normally ditributed
```

    Draw histogram of 1000 PRGN exponentials
    
```{r}
hist(iid2,50)  #semi-normal because values can't go below zero for exponential
```