---
title: "Analysis of ToothGrowth data"
author: "Pranjal Mandhaniya"
date: "Thursday 22 January 2015"
output: html_document
---

- Load the ToothGrowth data and perform some basic exploratory data analyses.
    We did that by boxplots.

```{r}
data(ToothGrowth)

# Box and Whisker plot of Orange Juice w.r.t all
boxplot(len ~ dose, data = ToothGrowth,xlab = "Length",ylab="Dose",
        main = "Orange Juice subset",subset = supp == "OJ", col = "orange")

# Box and Whisker plot of Vitamin C w.r.t all
boxplot(len ~ dose, data = ToothGrowth,xlab = "Length",ylab="Dose",
        main = "Vitamin C subset",subset = supp == "VC", col = "blue")
```

- Provide a basic summary of the data.

```{r}
summary(ToothGrowth)
```

- Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
    * Examination w.r.t Suppliment type

```{r}
len_VC <- ToothGrowth[ToothGrowth$supp=="VC",]$len

#95 % CI for Vitamin C suppliment
mean(len_VC) + c(-1,1)*qnorm(.95)* sd(len_VC)/sqrt(length(len_VC))

len_OJ <- ToothGrowth[ToothGrowth$supp=="OJ",]$len

#95 % CI for Orange Juice suppliment
mean(len_OJ) + c(-1,1)*qnorm(.95)* sd(len_OJ)/sqrt(length(len_OJ))

# t-test hypothesis testing
t.test(len_OJ,len_VC)
```

    * Examination w.r.t Dose in milligrams.
    
```{r}
len_Dose_half <- ToothGrowth[ToothGrowth$dose==0.5,]$len

#95 % CI for 0.5 mg Dose
mean(len_Dose_half) + c(-1,1)*qnorm(.95)* sd(len_Dose_half)/sqrt(length(len_Dose_half))

len_Dose_one <- ToothGrowth[ToothGrowth$dose==1,]$len

#95 % CI for 1 mg Dose
mean(len_Dose_one) + c(-1,1)*qnorm(.95)* sd(len_Dose_one)/sqrt(length(len_Dose_one))


len_Dose_two <- ToothGrowth[ToothGrowth$dose==2,]$len

#95 % CI for 2 mg Dose
mean(len_Dose_two) + c(-1,1)*qnorm(.95)* sd(len_Dose_two)/sqrt(length(len_Dose_two))
```

### Conclusion
    
```{r}
aggdt <- aggregate(len~(supp+dose),data = ToothGrowth,mean)
library(ggplot2)
ggplot()+ geom_line(data = aggdt,aes(x = len,y =dose,group = supp,colour = supp))
```


1. From our analysis we conclude that with increase in dosage the Tooth length increases.
    
2. Also Orange Juice suppliment performs better than Ascorbic acid(direct Vitamin C) in all dosages but mostly similar at 2 mg dosage.